DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-10-27 2015CompleteDerivation/completeDerivation.tex
First pass at all quantum justifications

\begin{justification}
	TODO
\end{justification}

@@

\begin{prop}\label{prop:wavefuntion}
	The state space $\Psi$ for an irreducible material is isomorphic to a subspace of the space of Lebesgue square integrable differentiable. That is $\Psi \cong \Psi(\mathcal{Q}, dp^i) \subseteq C^1(\mathcal{Q}) \cap L^2(\mathcal{Q}, \mu)$ under the isomorphism $\Upsilon_q : \Psi \leftrightarrow \Psi(\mathcal{Q}, dp^i)$ where $\Psi(\mathcal{Q}, dp^i)$ is the space of wave functions over $q^i$. The state space for a quantum particle is the projective space $\mathsf{P}(\Psi)$.
\end{prop}
\begin{justification}
	TODO
\end{justification}

@@

\begin{prop}\label{prop:inner_product}
	The state space $\Psi$ for an irreducible material is an inner product $\langle \cdot |\cdot \rangle : \Psi \times \Psi \rightarrow \mathbbm{C}$ such that $\langle \psi_1 | \psi_2 \rangle = \int_\mathcal{Q} \psi_1^\dagger (q^i) \psi_2(q^i) dq^i$.
\end{prop}
\begin{justification}
	TODO
\end{justification}

@@

\begin{prop}\label{prop:self_adjoint_operators}
	For each fragment variable $f$ there exists a corresponding self-adjoint linear operator $F : \Psi \rightarrow \Psi$. There exist a manifold $\hat{\mathcal{Q}}$ such that $f : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$ and $\Upsilon_{\hat{\mathcal{q}}^i} : \Psi \leftrightarrow \Psi(\hat{\mathcal{Q}}, d\hat{q}^i)$ is an isomorphism.
\end{prop}
\begin{justification}
	TODO
\end{justification}

@@

\begin{prop}\label{prop:momentum_operator}
	The operator $P_i$ associated with the conjugate quantity of $q^i$ is $P_i = - \imath \hbar \partial_{i}$. The operator that changes the variable of the wave function from $q^i$ to $p^i$ is $\Upsilon^{q_i}_{p^i} (\psi(q^i)) = \frac{1}{(\sqrt{2\pi})^3} \int_{\mathcal{Q}} e^{\frac{q_i p^i }{\imath \hbar}} \psi(q^i) d^n q $.
\end{prop}
\begin{justification}
	TODO
\end{justification}

@@

\begin{thrm}\label{thrm:inner_product}
	Let $V$ be a complex vector space. Let $| \cdot | ^2 : V \rightarrow \mathbbm{R}$ such that $|x|^2 \ge 0 \; \forall x \in V$ and $|x|^2 = 0 \Leftrightarrow x = 0$. Let $x \in V$ and $\mathsf{P}_x : V \rightarrow V$ be a family of projections (i.e. $\mathsf{P}_x$ linear and $\mathsf{P}_x \circ \mathsf{P}_x = \mathsf{P}_x$) such that: $\mathsf{P}_x (y) = y \Leftrightarrow y = a x$ for some $a \in \mathbbm{C}$; $|y|^2|\mathsf{P}_x (y)|^2=|x|^2|\mathsf{P}_y (x)|^2$; $\mathsf{P}_x (\mathsf{P}_y (x)) = r x$ for some $r \in \mathbbm{R}$.
	Then $V$ is an inner product space with the product $\langle \cdot , \cdot \rangle : V \times V \rightarrow \mathbbm{C}$ defined by $\langle x , y \rangle x = |x|^2 \mathsf{P}_x (y)$.
\end{thrm}

@@

\begin{thrm}
	Let $G \equiv C^1(\mathcal{Q}, \mathbbm{C}) \cap L^1(\mathcal{Q}, \mathbbm{C})$ be the space of differentiable and integrable complex functions defined over $\mathcal{Q}$. Let $K$ be a linear adjoint operator of the form $a \partial_q$ with $a \in \mathbbm{C}$. Let $K$ be self-adjoint with respect to the inner product $\langle f, g \rangle = 
	\int_{\mathcal{Q}} f^\dagger(q) g(q) dq$. Then $K= \imath r \partial_q$ with $r \in \mathbbm{R}$.
\end{thrm}

>>>>

\begin{justification}
	We claim $\Psi$ is an abelian group. $\Psi$ is the state space for a decomposable homogeneous material and is therefore an abelian group  by \ref{prop:abelian_group}.

	We claim the set of physically distinguishable transformations $T$ that change the unstated part of an irreducible material is isomorphic to $\mathbbm{C}$. Consider an amount $a_m \in \mathbbm{R}$ of irreducible material characterized by one d.o.f. The configuration of a fragment is characterized by two random variables $A, B: \Omega \rightarrow \mathbbm{R}$ where $\Omega$ is the sample space for the configuration of the fragments. As the configuration of each fragment is physically indistinguishable, $A$ and $B$ can be chosen such that the distribution $\rho$ of material over such variables is uniform and unitary. We can also rescale $A$ and $B$ such that they are defined on the range $[0, \sqrt{a_m}]$. We have $a_m=\int \rho dA \wedge dB = \int dA \wedge dB$. Consider a second amount $\hat{a}_m$ of irreducible material in the same configuration. It also can be characterized by a uniform distribution over two variables $C, D: \Omega \rightarrow \mathbbm{R}$ over a range of $\sqrt{\hat{a}_m}$. As the two amounts of material are in the same configuration we have $(C,D)$ is a function of $(A,B)$. We have $\hat{a}_m = \int dC \wedge dD = \int |J| dA \wedge dB$ where $|J|$ is the Jacobian determinant. As both distributions are uniform, $|J|$ has to be constant. The transformation has to be linear: $C=aA + bB$ and $D=-bA + aB$. As the amount of material is the only physically distinguishable quantity and is fully specified by $a$ and $b$, no other transformation is physically relevant. Let $\tau: \mathbbm{C} \rightarrow T$ represent such a transformation parametrized by $c=a+\imath b$. $|c|^2 = (a^2 + b^2) = \hat{a}_m / a_m$ is physically distinguishable. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{C}$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. The phase $arg(c)$ under addition is physically distinguishable as it can affect the modulus of the result. $\tau$ is an isomorphism between $T$ and $\mathbbm{C}$ as fields. Generalizing to multiple independent d.o.f. the set of transformation remains the same. The transformation on each d.o.f. is similarly defined by $c_i \in \mathbbm{C}$. As $\hat{a}_m / a_m$ is the same under all d.o.f. $|c_i|=|c_j|$. That has to always hold under addition as well, therefore $arg(c_i) = arg(c_j)$. $T\cong \mathbbm{C}$ even in multiple d.o.f.

	We claim $\Psi$ is a vector space over $\mathbbm{C}$. The abelian group $\Psi$ can be extended with the operations defined by $T$ as done in \ref{classical_vector space} for the infinitesimally reducible case.

@@

\begin{prop}\label{prop:wavefuntion}
	The state space $\Psi$ for an irreducible material is isomorphic to a subspace of the space of Lebesgue square integrable differentiable. That is $\Psi \cong \Psi(\mathcal{Q}, dp^i) \subseteq C^1(\mathcal{Q}) \cap L^2(\mathcal{Q}, \mu)$ under the isomorphism $\Upsilon_q : \Psi \leftrightarrow \Psi(\mathcal{Q}, dp^i)$ where $\Psi(\mathcal{Q}, dp^i)$ is the space of wave functions over $q^i$. The state space for a quantum particle is isomorphic to the projective space $\mathsf{P}(\Psi)$.
\end{prop}

\begin{justification}
	We claim the manifold $\mathcal{Q}$ that defines the units to describe a fragment of an irreducible material also provides a maximal description for the fragment configuration, that is: no other state variables can be added. Let $\mathcal{Q}$ be the manifold that defines the units. Then for each state $\psi \in \Psi$ there exists a distribution $\rho_\psi(q^i)$ that represents the quantity of material at each point. Suppose this distribution didn't represent a maximal description for the fragments. Then another independent variable $k$ would exist such that for each state $\psi \in \Psi$ we would have a distribution $\rho_\psi(q^i, k)$. $k$ cannot be part of a new d.o.f. as it would use a unit defined independently from $\mathcal{Q}$. This is a contradiction as $\mathcal{Q}$ defines all units. $k$ cannot lie in the same d.o.f. of one of the $q^i$ or it would provide a complete description for the fragment. This is a contradiction as the material is irreducible. $\mathcal{Q}$ provides a maximal description.

	We claim $\Psi \cong \Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ as a vector space. The maximal physical description of a set of fragments is given by a point in $\mathcal{Q}$ parametrized by $q^i$ and by a transformation in $T$ parametrized by $c \in \mathbbm{C}$. For each $\psi \in \Psi$ there must exist a wave function $\psi(q^i) : \mathcal{Q} \rightarrow \mathbbm{C}$ that provides the maximal physical description for the fragments. $\rho_\psi(q^i) = |\psi(q^i)|^2$ as the modulus of $\psi(q^i)$ is the increase/decrease from the unit amount of material. $\rho_\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$ by \ref{continuous_map}. Therefore $\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$. $\rho_\psi(q^i) \in L^1(\mathcal{Q}, \mu, \mathbbm{R})$ by the same arguments in the justification for \ref{integration}. Therefore $\psi(q^i) \in L^2(\mathcal{Q}, \mu, \mathbbm{C})$. Let $\Upsilon_{q^i} : \Psi \rightarrow C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ be the function that given a state returns its wave function. As the wave function capture the maximal description of the system, two states must represent different distributions. $\forall \psi_1, \psi_2 \in \Psi, \psi_1 \neq \psi_2 \implies \Upsilon_{q^i}(\psi_1) \neq \Upsilon_{q^i}(\psi_2)$. $\Upsilon_{q^i}$ is injective. $\Upsilon_{q^i}$ is a bijection between $\Psi$ and $\Psi(\mathcal{Q}, dp^i)\equiv\Upsilon_{q^i}(\Psi)$. Let $\psi=\psi_1+\psi_2$, then $\Upsilon_{q^i}(\psi)=\Upsilon_{q^i}(\psi_1)+\Upsilon_{q^i}(\psi_2)$ as combining the distributions means combining the statistical description of the fragments. Let $\psi_1=\tau(c)\psi_2$, then $\Upsilon_{q^i}(\psi_1)=c \Upsilon_{q^i}(\psi_2))$ as $\tau(c)$ transforms the fragment configuration by the factor $C$. $\Upsilon_{q^i}$ is a homomorphism as a vector space. $\Psi$ is isomorphic to $\Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$.

	We claim the state space for a quantum particle is isomorphic to the projective space $\mathsf{P}(\Psi)$. Let $\psi \in \Psi$ be the state of a quantum particle. $e^{\imath \theta} \psi$ with $\theta \in \mathbbm{R}$ is not physically distinguishable from $\psi$ as phases are only physically distinguishable through addition. $\sqrt{\rho} \psi$ with $\sqrt{\rho} \in \mathbbm{R}^+$ cannot represent a quantum particle as it as a different amount of material. There exists only one distinguishable state for a quantum particle in the equivalence class $\psi \sim c \psi$ with $c \in \mathbbm{C}$. The state with no amount of material does not correspond to any particle state. The quotient space $\mathsf{P}(\Psi) \equiv (\Psi - \{0\}) / \sim$ is isomorphic to the state of quantum particles.
\end{justification}

@@

\begin{prop}\label{prop:inner_product}
	The state space $\Psi$ for an irreducible material is an inner product with $\langle \cdot |\cdot \rangle : \Psi \times \Psi \rightarrow \mathbbm{C}$ such that $\langle \psi_1 | \psi_2 \rangle = \int_\mathcal{Q} \psi_1^\dagger (q^i) \psi_2(q^i) dq^i$.
\end{prop}
\begin{justification}
	We claim there is exists a map $| \cdot | ^2 : \Psi \rightarrow \mathbbm{R}$ such that $|\psi|^2 \ge 0 \; \forall \psi \in \Psi$ and $|\psi|^2 = 0 \Leftrightarrow \psi = 0$. Let $| \cdot | ^2 : \Psi \rightarrow \mathbbm{R}$ be the map that returns the amount of material for a given state. Let $\psi \in \Psi$ and $c \in \mathbbm{C}$. $|\tau(c) \psi|^2 = |c|^2 |\psi|^2$ as $\tau(c)$ increases the amount of material by $|c|^2$, which is always positive. $|\psi|^2 \ge 0 \; \forall \psi \in \Psi$. $|\psi|^2 = 0 \Leftrightarrow \psi = 0$ as the only state with no material is the empty state.

	We claim $\forall \psi \in \Psi$ there exist a projection $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ with $\psi \in \Psi$. Let $\psi \in \Psi$ be a state. Let $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ be an operator that returns the part of a given state that is prepared as $\psi$. $\mathsf{P}_{\psi}(c_1 \phi_1 + c_2 \phi_2) = c_1 \mathsf{P}_{\psi}(\phi_1) + c_2 \mathsf{P}_{\psi}(\phi_2)$ is linear as the part of the composition prepared like $\psi$ is the composition of the parts so prepared. $\mathsf{P}_\psi \circ \mathsf{P}_\psi = \mathsf{P}_\psi$ is a projection because the whole $\mathsf{P}_\psi$  is prepared as $\psi$.

	We claim $\mathsf{P}_{\psi} (\phi) = \phi \Leftrightarrow \phi = c \psi$ for some $c \in \mathbbm{C}$. Let $\psi, \phi \in \Psi$ such that $\mathsf{P}_{\psi} (\phi) = \phi$. The whole state $\phi$ is prepared as $\psi$. We can obtain $\phi$ from $\psi$ by a transformation in the unstated part. $\phi = c \psi$ for some $c \in \mathbbm{C}$. Let $\psi, \phi \in \Psi$ such that $\phi = c \psi$ for some $c \in \mathbbm{C}$. Then all of $\phi$ is prepared as $\psi$. $\mathsf{P}_{\psi} (\phi) = \phi$. Therefore $\mathsf{P}_{\psi} (\phi) = \phi \Leftrightarrow \phi = c \psi$.

	We claim $|\psi|^2|\mathsf{P}_{\psi} (\phi)|^2=|\phi|^2|\mathsf{P}_{\phi} (\psi)|^2$. Let $\psi, \phi \in \Psi$. As the material is irreducible, $\psi$ and $\phi$ cannot be used to describe smaller parts. The fraction of $\phi$ that is prepared as $\psi$ must be equal to the fraction of $\psi$ that is prepared as $\phi$. $\frac{|\mathsf{P}_{\psi} (\phi)|^2}{|\phi|^2}=\frac{|\mathsf{P}_{\phi} (\psi)|^2}{|\psi|^2}$.

	We claim $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}$. Let $\psi, \phi \in \Psi$. Consider $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi))$: we first take the part of $\psi$ prepared like $\phi$ and then take the part of that prepared like $\psi$. The overall operation is simply returning a part of $\psi$. These must correspond to the same exact configuration for the fragments. The only thing that can change is the amount of material. Therefore $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}^+$.

	We claim that the state space $\Psi$ for an irreducible material has an inner product $\langle \cdot |\cdot \rangle : \Psi \times \Psi \rightarrow \mathbbm{C}$. $| \cdot | ^2$ and $\mathsf{P}_{\phi}$ satisfy the requirements in \ref{thrm:inner_product}. $\Psi$ is an inner product space with $\langle \cdot |\cdot \rangle : \Psi \times \Psi \rightarrow \mathbbm{C}$ such that $\langle \psi |\phi \rangle \psi = | \psi | ^2\mathsf{P}_{\psi}(\phi)$.

	We claim that the inner product can be expressed in terms of the wave functions as $\langle \psi_1 | \psi_2 \rangle = \int_\mathcal{Q} \psi_1^\dagger (q^i) \psi_2(q^i) dq^i$. The amount of material associated with a state $\psi \in \Psi$ is $\langle \psi | \psi \rangle = | \psi |^2 = \int_\mathcal{Q} \psi^\dagger (q^i) \psi(q^i) dq^i$. The inner product associated with the $L^2$ norm is $\int_\mathcal{Q} \psi_1^\dagger (q^i) \psi_2(q^i) dq^i$ with $\psi_1, \psi_2 \in \Psi$. Therefore $\langle \psi_1 | \psi_2 \rangle = \int_\mathcal{Q} \psi_1^\dagger (q^i) \psi_2(q^i) dq^i$.

@@

\begin{prop}\label{prop:self_adjoint_operators}
	For each fragment variable $f$ there exists a corresponding self-adjoint linear operator $F : \Psi \rightarrow \Psi$ such that $\langle \psi | F \psi \rangle$ is the expectation of $f$ multiplied by the amount of material. There exist a topological space $\hat{\mathcal{Q}}$ such that $q^1 \equiv f : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$ and a vector space isomorphism $\Upsilon_{\hat{\mathcal{q}}^i} : \Psi \leftrightarrow \Psi(\hat{\mathcal{Q}}, d\hat{q}^i)$ where $\Psi(\hat{\mathcal{Q}}, d\hat{q}^i)$ is the space of wave functions over $\hat{\mathcal{Q}}$.
\end{prop}
\begin{justification}
	We claim for each fragment variable $f$ there exist a topological space $\hat{\mathcal{Q}}$ such that $f : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$. Let $f$ be a fragment variable. Let $\hat{q}^i$ be a set of fragment variables such that $\hat{q}^1\equiv f$. If $\hat{q}^i$ does not provide a maximal description of $f$ then there exists another set of fragment variables. Extend $\hat{q}^i$ with such variables. As the number of possibilities charted by $\hat{q}^i$ cannot exceed the number of possibilities charted by $q^i$, at some point we'll reach a maximal description. We call $\hat{\mathcal{Q}}$ the topological space charted by the fragment variables $\hat{q}^i$.

	We claim there exists a vector space isomorphism $\Upsilon_{\hat{\mathcal{q}}^i} : \Psi \leftrightarrow \Psi(\hat{\mathcal{Q}}, d\hat{q}^i)$. Let $\psi \in \Psi$ be a state. $q^i$ provides a maximal description for the fragments. There must exist a $\psi(q^i) : \mathbbm{R}^n \rightarrow \mathbbm{C}$ associated with $\psi$ such that it gives the fragment configuration at a particular value for $q^i$. Such wave function provides a full description for the state. Let $\Upsilon_{\hat{\mathcal{q}}^i} : \Psi \rightarrow \Psi(\hat{\mathcal{Q}}, d\hat{q}^i)$ the map that associates a state with its wave function over $\hat{\mathcal{Q}}$. $\Upsilon_{\hat{\mathcal{q}}^i}$ is a vector space isomorphism for the same reason discussed in \ref{prop:wavefuntion}

	We claim there exist a self-adjoint linear operator $F : \Psi \rightarrow \Psi$ such that $\langle \psi | F \psi \rangle$ is the expectation of $f$ multiplied by the amount of material. Let $f$ be a fragment variable. The expectation value multiplied by the amount of material is given by $\int f \rho(f) df$ where $\rho(f)$ is the density of material in $f$. Let $q^i$ a set of fragment variables that provides a maximal description for the fragments. Let $q^1 = f$ and $k=2,...,n$. We have $\rho(f) = \int \psi^\dagger(f, q^k) \psi(f, q^k) dq^{n-1}$. $\int f df \int \psi^\dagger(f, q^k) \psi(f, q^k) dq^{n-1} = \int \psi^\dagger(q^i) f(q^i) \psi(q^i) dq^{n}$. $f$ is a linear operator on the space of the wave function over $\hat{\mathcal{Q}}$ that increases the module at each point. TODO. Therefore $f(q^i) \psi(q^i) \in \Psi(\hat{\mathcal{Q}})$. As $\Upsilon_{\hat{\mathcal{q}}^i}$ is an isomorphism, there exists a linear operator $F : \Psi \rightarrow \Psi$ such that $f(q^i) \psi(q^i) = f(q^i) \Upsilon_{\hat{\mathcal{q}}^i}(\psi) = \Upsilon_{\hat{\mathcal{q}}^i}(F \psi)$. $\langle F \psi | \psi \rangle = \int (f(q^i) \psi(q^i))^\dagger \psi(q^i) = \int \psi^\dagger(q^i) f(q^i) \psi(q^i) = \langle \psi | F \psi \rangle$: $F$ is self-adjoint.
\end{justification}

@@

\begin{prop}\label{prop:momentum_operator}
	The operator $P_i$ associated with the conjugate quantity of $q^i$ is $P_i = - \imath \hbar \partial_{i}$. The operator that changes the variable of the wave function from $q^i$ to $p_i$ is $\Upsilon^{q^i}_{p_i} (\psi(q^i)) = \frac{1}{(\sqrt{2\pi})^3} \int_{\mathcal{Q}} e^{\frac{q^i p_i }{\imath \hbar}} \psi(q^i) d^n q $. The space of wave functions $\Psi(\mathcal{Q}, dq^i) = S(\mathcal{Q}, q^i)$ where $S(\mathcal{Q}, q^i)$ is the Schwartz space of rapidly decreasing smooth functions. 
\end{prop}
\begin{justification}
	We claim the operator associated with $k_i$ is $K_i = - \imath \partial_{i}$. Let $K_i : \Psi(\mathcal{Q}, dq^i) \rightarrow \Psi(\mathcal{Q}, dq^i)$ the linear operator associated with $k_i$ as express on the space of wave functions over $q^i$. Such operator must be covariant under the transformation $\hat{q}^i = \hat{q}^i(q^i)$. That is: $K_{\hat{q}^i} = \partial_{\hat{q}^i}q^iK_{q^i}$. By \ref{thrm:covariant_operator} $K_i=c\partial_i$ for some $c \in \mathbbm{C}$. $K_i$ is hermitian: $K_i=\imath r\partial_i$ for some $r \in \mathbbm{R}$ by \ref{thrm:antihermitian_derivative}. $k_i$ is expressed in units of inverse $q^i$ therefore $|r|=1$. By convention, we choose $r$ to be negative. $K_i = - \imath \partial_{i}$.

	We claim the operator associated with $p_i$ is $P_i = - \imath \hbar \partial_{i}$. As $p_i=\hbar k_i$, their expectation is proportional by $\hbar$. $P_i=\hbar K_i= -\imath \hbar \partial_i$.

	We claim the operator that changes the variable of the wave function from $q^i$ to $p_i$ is $\Upsilon^{q^i}_{p_i} (\psi(q^i)) = \frac{1}{(\sqrt{2\pi})^3} \int_{\mathcal{Q}} e^{\frac{q^i p_i }{\imath \hbar}} \psi(q^i) d^n q $. Let $\Upsilon^{q_i}_{p^i} : \Psi(\mathcal{Q}, dq^i) \rightarrow \Psi(\mathcal{P}, dp^i)$ the operator that maps a wave function over $\mathcal{Q}$ into a wave function over $\mathcal{P}$, the space charted by $p_i$. $\Upsilon^{q_i}_{p^i}$ must exist and be unique (up to a total phase) as $\Upsilon^{q_i}_{p^i} = \Upsilon_{p^i}\Upsilon^{q_i} = \Upsilon_{p^i}(\Upsilon_{q_i})^{-1}$ is an isomorphism. $\Upsilon^{q_i}_{p^i}$ must be a linear transform that takes the operator $P_i= - \imath \hbar \partial_i$ as expressed over $q^i$ to $P_i = p_i$ as expressed over $p_i$. Such transformation is the Fourier transform. $\Upsilon^{q^i}_{p_i} (\psi(q^i)) = \frac{1}{(\sqrt{2\pi})^3} \int_{\mathcal{Q}} e^{\frac{q^i p_i }{\imath \hbar}} \psi(q^i) d^n q $.

	We claim $\Psi(\mathcal{Q}, dq^i) \subseteq S(\mathcal{Q}, q^i)$. Let $\psi(q^i) \in \Psi(\mathcal{Q}, dq^i)$. $P_i^n \psi(q^i) = (-\imath \hbar \partial_i)^n \psi(q^i)$ represents the n-th power of the conjugate momentum operator applied to the given state. As the quantity is physical, such operation must be defined for any $n$ therefore $\psi(q^i) \in C^\infty(\mathcal{Q})$. Let $\psi(p_i) = \Upsilon^{q^i}_{p_i} (\psi(q^i))$ be the wave function over momentum space. $(Q^i)^n \psi(p_i) = (+\imath \hbar \partial_{p_i})^n \psi(p_i)$ represents the n-th power of the $q^i$ operator applied to the given state. As the quantity is physical, such operation must be defined for any $n$ therefore $\psi(p_i) \in C^\infty(\mathcal{P})$. As $\psi(q^i)$ is the Fourier transform of an infinitely smooth function, it decreases faster then any inverse power of $q^i$. That is: $\forall m \in \mathbbm{Z}^+ \exists c \in \mathbbm{C}$ such that  $|\psi(q^i)|<\frac{c}{|q^i|^m} \; \forall |q^i|> 1$. $\Psi(\mathcal{Q}, dq^i) \subseteq S(\mathcal{Q}, q^i)$.

	We claim $\Psi(\mathcal{Q}, dq^i) = S(\mathcal{Q}, q^i)$. Let $\psi(q^i) \in \Psi(\mathcal{Q}, dq^i)$ and $\hat{\psi}(q^i) \in S(\mathcal{Q}, q^i)$ such that $\psi(q^i) \neq \hat{\psi}(q^i)$. There exists $a, b \in \mathbbm{Z}^+$ such that, for a given $i$, $\lVert \psi(q^i) - \hat{\psi}(q^i) \rVert_{i,a,b} \neq 0$  where $\lVert \psi(q^i) \rVert = sup|(q^i)^a (\partial_i) ^b \psi(q^i)|$. The operator $(Q^i)^a(P_i)^b$ applied to the two functions will provide different distributions for the associated fragment variables. $\hat{\psi}(q^i)$ is physically distinguishable and is associated with a physical state. $\hat{\psi}(q^i) \in \Psi(\mathcal{Q}, dq^i)$
\end{justification}

@@

\begin{thrm}\label{thrm:inner_product}
	Let $V$ be a complex vector space. Let $| \cdot | ^2 : V \rightarrow \mathbbm{R}$ such that $|x|^2 \ge 0 \; \forall x \in V$ and $|x|^2 = 0 \Leftrightarrow x = 0$. Let $x \in V$ and $\mathsf{P}_x : V \rightarrow V$ be a family of projections (i.e. $\mathsf{P}_x$ linear and $\mathsf{P}_x \circ \mathsf{P}_x = \mathsf{P}_x$) such that: $\mathsf{P}_x (y) = y \Leftrightarrow y = a x$ for some $a \in \mathbbm{C}$; $|x|^2|\mathsf{P}_x (y)|^2=|y|^2|\mathsf{P}_y (x)|^2$; $\mathsf{P}_x (\mathsf{P}_y (x)) = r x$ for some $r \in \mathbbm{R}$.
	Then $V$ is an inner product space with the product $\langle \cdot , \cdot \rangle : V \times V \rightarrow \mathbbm{C}$ defined by $\langle x , y \rangle x = |x|^2 \mathsf{P}_x (y)$.
\end{thrm}

@@

\begin{thrm}\label{thrm:antihermitian_derivative}
	Let $G \equiv C^1(\mathcal{Q}, \mathbbm{C}) \cap L^1(\mathcal{Q}, \mathbbm{C})$ be the space of differentiable and integrable complex functions defined over $\mathcal{Q}$. Let $K$ be a linear adjoint operator of the form $a \partial_q$ with $a \in \mathbbm{C}$. Let $K$ be self-adjoint with respect to the inner product $\langle f, g \rangle = 
	\int_{\mathcal{Q}} f^\dagger(q) g(q) dq$. Then $K= \imath r \partial_q$ with $r \in \mathbbm{R}$.
\end{thrm}
